On the Design of Communication and Transaction Anonymity in Blockchain-Based Transactive Microgrids

### 2017-10-16 docs/papers/Serial2017/communicationanonymity.tex
fixed typos in SERIAL'17

In practice, the deployment of onion routing (or a variant thereof called garlic routing) in the Invisible Internet Project (I2P) works as follows. Each node in the network operates an I2P router, allowing for anonymous communications. A router is distinct from an endpoint application in that it is not a secret who runs a router. By contrast, an application is the destination for the communications and is anonymous.  This disconnect allows for a higher degree of anonymity. To communicate between routers, unidirectional tunnels are set up. The tunnels use layered encryption, meaning that each router in the tunnel only can decrypt one layer. In order to transmit a message between two routers, the sender needs to know  where to direct the message, i.e. what the address of the entry point of the receiver is.

The I2P protocol differs from regular network communications in that, for communications to take place between routers, each router needs to know a structure called the \textit{RouterInfo}. It contains the 2048-bit ELGamal encryption key, a signing key, a certificate, timestamp, text field, signature of bundle and the contact addresses where a router can be reached. The RouterInfo is given along with something called a \textit{LeaseSet}, containing a group of tunnel entry points for a particular client destination, when the tunnel will expire, the destination itself, encryption key for end-to-end encryption of garlic messages, revocation key and a signature of the LeaseSet data. The LeaseSet identifies an application on the I2P network. The I2P protocol ensures the anonymity of its users because of the disconnect between the identities of the applications communicating over the network, and the identities of the routers. This metadata is stored in a distributed directory called the netDb, based on the Kademlia P2P-protocol, which describes a provably consistent and fault-tolerant distributed hash table. \cite{kademlia} The RouterInfo and LeaseSet data are stored on the netDb under the key derived from the SHA256 of the destination.

>>>>

In practice, the deployment of onion routing (or a variant thereof called garlic routing) in the Invisible Internet Project (I2P) works as follows. Each node in the network operates an I2P router, allowing for anonymous communications. A router is distinct from an endpoint application in that it is not a secret who runs a router. By contrast, an application is the destination for the communications and is anonymous.  This disconnect allows for a higher degree of anonymity. To communicate between routers, unidirectional tunnels are set up. The tunnels use layered encryption, meaning that each router in the tunnel only can decrypt one layer. In order to transmit a message between two routers, the sender needs to know  where to direct the message, i.e., what the address of the entry point of the receiver is.

The I2P protocol differs from regular network communications in that, for communications to take place between routers, each router needs to know a structure called the \textit{RouterInfo}. It contains the 2048-bit ELGamal encryption key, a signing key, a certificate, timestamp, text field, signature of bundle and the contact addresses where a router can be reached. The RouterInfo is given along with something called a \textit{LeaseSet}, containing a group of tunnel entry points for a particular client destination, when the tunnel will expire, the destination itself, encryption key for end-to-end encryption of garlic messages, revocation key and a signature of the LeaseSet data. The LeaseSet identifies an application on the I2P network. The I2P protocol ensures the anonymity of its users because of the disconnect between the identities of the applications communicating over the network, and the identities of the routers. This metadata is stored in a distributed directory called the netDb, based on the Kademlia P2P-protocol, which describes a provably consistent and fault-tolerant distributed hash table~\cite{kademlia}. The RouterInfo and LeaseSet data are stored on the netDb under the key derived from the SHA256 of the destination.

### 2017-10-16 docs/papers/Serial2017/intro.tex
fixed typos in SERIAL'17

Transactive energy models have been proposed as a set of market based mechanisms for balancing the demand and generation of energy in communities \cite{kok2016society,cox2013structured,melton2013gridwise}.
 In this approach, customers on the same feeder (i.e. sharing a power line link) can operate in an open market, trading and exchanging generated energy locally. Distribution System Operators can be the custodian of this market, while still meeting the net demand \cite{7462854}. Blockchains have  recently emerged as a foundation for enabling the transactional service in the microgrids. For example, the Brooklyn Microgrid
(\url{brooklynmicrogrid.com}) is a peer-to-peer market for locally
generated renewable energy, which was developed by LO3 Energy as a pilot project. Similarly, RWE, and Grid Singularity have developed blockchain based solutions for incentivizing neighbors to sell excess energy to the grid and payments for electric car charging %and (c) enabling pre-paid transactions for electric bills in South Africa, respectively. 
However, those solutions do not address the requirements for off-blockchain communication network and the requirements for privacy.

@@

The outline of this paper is as follows. We first present an overview of the PETra workflow described in \cite{Laszka17} in Section \ref{sec:petra}. We then discuss the communication anonymity extensions in Section \ref{comm} and transaction anonymity in Section \ref{trans}. Section \ref{commthreat} discusses the threat vectors for the communication anonymity approach. Section \ref{transthreat} describes the transaction anonymity threats.
Finally, we provide concluding remarks in Section~\ref{sec:discussion}.

>>>>

Transactive energy models have been proposed as a set of market based mechanisms for balancing the demand and generation of energy in communities \cite{kok2016society,cox2013structured,melton2013gridwise}.
 In this approach, customers on the same feeder (i.e. sharing a power line link) can operate in an open market, trading and exchanging generated energy locally. Distribution System Operators can be the custodian of this market, while still meeting the net demand \cite{7462854}. Blockchains have  recently emerged as a foundation for enabling the transactional service in the microgrids. For example, the Brooklyn Microgrid
(\url{brooklynmicrogrid.com}) is a peer-to-peer market for locally
generated renewable energy, which was developed by LO3 Energy as a pilot project. Similarly, RWE, and Grid Singularity have developed blockchain based solutions for incentivizing neighbors to sell excess energy to the grid and payments for electric car charging. %and (c) enabling pre-paid transactions for electric bills in South Africa, respectively. 
However, those solutions do not address the requirements for off-blockchain communication network and the requirements for privacy.

@@

The outline of this paper is as follows. We first present an overview of the PETra workflow described in \cite{Laszka17} in Section \ref{sec:petra}. We then discuss the communication anonymity extensions in Section \ref{comm} and transaction anonymity in Section \ref{trans}. Section \ref{commthreat} discusses the threat vectors for the communication anonymity approach. Section~\ref{transthreat} describes the transaction anonymity threats.
Finally, we provide concluding remarks in Section~\ref{sec:discussion}.

### 2017-10-16 docs/papers/Serial2017/paper.tex
fixed typos in SERIAL'17

\begin{abstract}
%\textcolor{red}{The abstract needs to be rewritten}
%Transactive microgrids are emerging as the next  advancement for power grid. They provide robust capabilities for integrating distributed generation resources in communities, creat
 Transactive microgrids are emerging as a transformative solution for the problems faced by distribution system operators due to an increase in the use of distributed energy resources and a rapid acceleration in renewable energy generation, such as wind and solar power. Distributed ledgers have recently found widespread interest in this domain due to their ability to provide transactional integrity across decentralized computing nodes. However, the existing state of the art has not focused on the privacy preservation requirement of these energy systems --  the transaction level data can provide much greater insights into a prosumer's behavior compared to smart meter data. %\Aron{We could also mention safety requirements as a challenge to privacy (for stable grid control, we need to disseminate information).}\Jonatan{Resolved} 
 There are specific safety requirements in transactive microgrids to ensure the stability of the grid and to control the load. To fulfil these requirements, the distribution system operator needs transaction information from the grid, which poses a further challenge to the privacy-goals. This problem is made worse by requirement for off-blockchain communication in these networks. In this paper, we extend a recently developed trading workflow called PETra and describe our solution for communication and transactional anonymity.    
 %exacerbated further by consideration that 
 %Blockchains is an emerging technology that has found widespread interest in this domain  These, on one hand, pose a decentralized power system controls problem, requiring strategic microgrid control to maintain stability for the community and for the utility. On the other hand, they require robust financial markets where transactions beneficial for the grid should be incentivized, while ensuring that erroneous transactions cannot destabilize the grid. 
% Successful setup and operation of these microgrids require a distributed transactive and control platform that works together to ensure that transactions of energy (a) are unforgeable in the sense that producers should not be able to create a transaction without actually producing energy, (b) are tamper proof, and (c) preserve the anonymity of the actors.
 % This last point is crucial because  the transaction level data can provide much greater insights into a prosumer's behavior compared to smart meter data. \Aron{This is the first mention of blockchains. If we are targeting SERIAL, then I think that the abstract needs to be more focused on blockchains and distributed ledgers. Maybe include them in the title as well?} In this paper, we first describe the use of blockchains to create a transactional workflow that satisfy the first two requirements. The third requirement are met by

>>>>

\begin{abstract}
%\textcolor{red}{The abstract needs to be rewritten}
%Transactive microgrids are emerging as the next  advancement for power grid. They provide robust capabilities for integrating distributed generation resources in communities, creat
 Transactive microgrids are emerging as a transformative solution for the problems faced by distribution system operators due to an increase in the use of distributed energy resources and a rapid acceleration in renewable energy generation, such as wind and solar power. Distributed ledgers have recently found widespread interest in this domain due to their ability to provide transactional integrity across decentralized computing nodes. However, the existing state of the art has not focused on the privacy preservation requirement of these energy systems --  the transaction level data can provide much greater insights into a prosumer's behavior compared to smart meter data. %\Aron{We could also mention safety requirements as a challenge to privacy (for stable grid control, we need to disseminate information).}\Jonatan{Resolved} 
 There are specific safety requirements in transactive microgrids to ensure the stability of the grid and to control the load. To fulfil these requirements, the distribution system operator needs transaction information from the grid, which poses a further challenge to the privacy goals. This problem is made worse by requirement for off-blockchain communication in these networks. In this paper, we extend a recently developed trading workflow called PETra and describe our solution for communication and transactional anonymity.    
 %exacerbated further by consideration that 
 %Blockchains is an emerging technology that has found widespread interest in this domain  These, on one hand, pose a decentralized power system controls problem, requiring strategic microgrid control to maintain stability for the community and for the utility. On the other hand, they require robust financial markets where transactions beneficial for the grid should be incentivized, while ensuring that erroneous transactions cannot destabilize the grid. 
% Successful setup and operation of these microgrids require a distributed transactive and control platform that works together to ensure that transactions of energy (a) are unforgeable in the sense that producers should not be able to create a transaction without actually producing energy, (b) are tamper proof, and (c) preserve the anonymity of the actors.
 % This last point is crucial because  the transaction level data can provide much greater insights into a prosumer's behavior compared to smart meter data. \Aron{This is the first mention of blockchains. If we are targeting SERIAL, then I think that the abstract needs to be more focused on blockchains and distributed ledgers. Maybe include them in the title as well?} In this paper, we first describe the use of blockchains to create a transactional workflow that satisfy the first two requirements. The third requirement are met by

### 2017-10-16 docs/papers/Serial2017/transactionanonymity.tex
fixed typos in SERIAL'17

\subsection{Transaction Anonymity}
\label{trans}
Communication anonymity is necessary but not sufficient for
anonymous trading, as the cryptographic objectives of authentication and legitimacy are not fulfilled. We suggest using cryptographic techniques from distributed ledgers, \textit{blockchains} and cryptocurrencies. The most adopted of which is the Bitcoin blockchain and currency. It allows for very simple digital cash spending but has serious privacy and anonymity flaws~\cite{Barber2012,Reid2013,apostolaki2017}. Additionally, Biryukov and Pustogarov, 2015, show that using Bitcoin over the Tor network opens an entirely new attack surface~\cite{biryukov2015}. Solutions to the tracing and identification problems identified by these researchers have been proposed and implemented in alternative cryptocurrency protocols: mixing using ring signatures and zero-knowledge proofs.~\cite{miers2013zerocoin,cryptonote}

\subsubsection{Mixing Through Ring Signatures}
The CryptoNote protocol prevents tracing assets back to their original owners by
mixing together multiple incoming transactions and multiple outgoing
transactions. This service thus hides the connections between the
prosumers and the anonymous addresses. Mixing requires the possibility to create new wallets at will, something that is generally recommended upon any cryptocurrency transfer and it requires the existence of a sufficient number of participants in the network. These protocols enable participants to
mix assets with each other, thereby eliminating the need for a trusted
third party. Monero is an example of a cryptocurrency that provides built-in mixing services by implementing the CryptoNote protocol.~\cite{cryptoeprint:2015:1098} There are however alternative implementations of mixing protocols such as CoinShuffle~\cite{ruffing2014coinshuffle} or
Xim~\cite{bissias2014sybil}.

@@

Group signatures were first introduced by Chaum and van Heyst, 1991,~\cite{Chaum1991} and then built upon by Rivest \textit{et al.}, 2001.~\cite{Rivest2001} The basis for anonymity in the CryptoNote protocol, however, is a slightly modified version of the \textit{Traceable ring signature} algorithm by Fukisaki and Suzuki, 2007.~\cite{Fujisaki2007} The algorithm allows a member of a group to send a transaction in such a way that it is impossible for a receiver to know any more about the sender than that it came from a group member without the use of a central authority.

@@

Additionally, if the receiver and sender have randomly generated, unique and new addresses, the Diffie-Hellman protocol can be used to generate a new pair of public-private keys. This is how untraceability of public keys is achieved. The sender should generate ephemeral keys for each transfer, enabling only the receiver to recover the corresponding private key. As an illustrative example, in Figure \ref{fig:ringsigs}, a schematic diagram shows households A, B and C signing a transaction since they are part of the same ring. A ring would, in reality, be many more households, not necessarily of the same microgrid. Let's assume that A is the true origin of the transaction. When E receives the transaction, the only thing that E can know with certainty is that one of A, B or C initiated the transaction. To increase the transaction anonymity further, a second, third or n rounds of ring signatures can be algorithmically imposed upon the network. With each round of signing parties, the group of potential origins grows linearly. Notably, the ring signature algorithm by Fujisaki and Suzuki, \cite{Fujisaki2007}, has been published in a peer-reviewed paper. This can be compared favorably to many cryptocurrency protocols which are simply published as white papers without any formal review-process. \cite{cryptonote}
In practice, a transaction using the mixing service should be performed in the following way to ensure anonymity:

@@

\subsubsection{Mixing through Zero-Knowledge Proofs}
Zero-knowledge proofs (ZKP) are ways for a person to prove the knowledge of some specific fact to a verifier, without actually having to disclose the knowledge. Blum \textit{et al.} provided non-interactive ZKPs (NIZK) in 1988 \cite{Blum:1988:NZA:62212.62222}, where the prover and verifier don't have to interact or communicate directly with each other. The Zerocoin protocol \cite{miers2013zerocoin} outlines a way how NIZKs can achieve the untraceability objective of the previous section and it ensures that no double-spending is allowed.\footnote{Each coin in the protocol is identified uniquely by a serial number.} Zerocoin is a protocol for the decentralized mixing of coins, so that they can not be traced, or \textit{tainted}. However, senders and destinations can still be identified.~\cite{miers2013zerocoin} Luckily, Zerocash~\cite{Sasson:2014:ZDA:2650286.2650810} extends the NIZK functionality to allow for anonymous transactions, anonymous balances and coins, improved performance of transactions and sending of assets to a receivers fixed address without action required from the receiver. Zerocash makes use of a more efficient version of the NIZK, used in Zerocoin, called ZK \textit{Succinct Non-interactive ARguments of Knowledge} (zk-SNARK). 
% It features the algorithms: \textbf{Setup($1^\lambda$)}$\rightarrow \textit{params}$, \textbf{Mint(}\textit{params})$\rightarrow \textit{(c,skc)}$, \textbf{Spend}(\textit{params, c, skc, R, \textbf{C}})$\rightarrow(\pi, S)$ and \textbf{Verify}(\textit{params, $\pi$, S, R, \textbf{C}})$\rightarrow$$\{$0,1$\}$. The \textbf{Setup} function takes a secret parameter and returns a global public set of parameters and description of the set of coins. It is only executed once in the lifetime of the scheme, and the authors of the protocol recommend the usage of a trusted party for this. \textbf{Mint} is used to create coins from the coin set, given the parameters. \textbf{Spend} and \textbf{Verify} are executed by a sender and a receiver, respectively at the beginning and end of each transaction.

@@

\subsubsection{Threats and weaknesses in Ring Signature- and Zero-Knowledge Proof-schemes}
\label{transthreat} 
\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{ringsigs.png}
\caption{Visualization of untraceability in ring signatures in smart meter-based energy trading and the potential deductions of origin of the transaction by a single household in the chain of signatures.}\label{fig:ringsigs}
\end{figure}
When applying either ring signatures or zero-knowledge SNARKs to PETra, potential weaknesses or attacks need to be considered.A potential threat to ring signatures is when a large amount of the unspent transactions are owned by an adversary or when insufficient amounts of signatures are included in a ring. When a prosumer A wishes to select a group of signatures to sign her transaction as well, then it is likely that she will select many of the transactions from the adversary. Assuming the adversary spends his outputs without \textit{mixing}\footnote{The number of other signatures used in the ring.}, then A's transaction is exposed as well.~\cite{monero2014} Recent research  also show that up to 65\% of Monero transactions are trivially traceable using one attack. They also exposes two more attacks that have been amended in the latest versions of the protocol, lowering the amount of transactions traceable to 20\%.~\cite{monero2014,DBLP:journals/corr/MillerMLN17}

One of the main weaknesses of the Zerocash-based protocol is that for each private transaction, a costly zk-SNARK needs to be computed. But that is not a threat to anonymity, just a practical reason why it might be difficult to run the scheme over a congested public blockchain. In \cite{Sasson:2014:ZDA:2650286.2650810}, experiments show an average time of 3 min to create the zk-SNARK for a private transaction, verifying it takes only 8.5 ms. Another large practical drawback of Zerocash is the lack of programmability and functionality that would be required in PETra. Zhang \textit{et al.} solve some of the practical flaws and amend security issues.~\cite{zhangz}

>>>>

\subsection{Transaction Anonymity}
\label{trans}
Communication anonymity is necessary but not sufficient for
anonymous trading, as the cryptographic objectives of authentication and legitimacy are not fulfilled. We suggest using cryptographic techniques from distributed ledgers, \textit{blockchains} and cryptocurrencies. The most adopted of which is the Bitcoin blockchain and currency. It allows for very simple digital cash spending but has serious privacy and anonymity flaws~\cite{Barber2012,Reid2013,apostolaki2017}. Additionally, Biryukov and Pustogarov, 2015, show that using Bitcoin over the Tor network opens an entirely new attack surface~\cite{biryukov2015}. Solutions to the tracing and identification problems identified by these researchers have been proposed and implemented in alternative cryptocurrency protocols: mixing using ring signatures and zero-knowledge proofs~\cite{miers2013zerocoin,cryptonote}.

\subsubsection{Mixing Through Ring Signatures}
The CryptoNote protocol prevents tracing assets back to their original owners by
mixing together multiple incoming transactions and multiple outgoing
transactions. This service thus hides the connections between the
prosumers and the anonymous addresses. Mixing requires the possibility to create new wallets at will, something that is generally recommended upon any cryptocurrency transfer and it requires the existence of a sufficient number of participants in the network. These protocols enable participants to
mix assets with each other, thereby eliminating the need for a trusted
third party. Monero is an example of a cryptocurrency that provides built-in mixing services by implementing the CryptoNote protocol~\cite{cryptoeprint:2015:1098}. There are however alternative implementations of mixing protocols such as CoinShuffle~\cite{ruffing2014coinshuffle} or
Xim~\cite{bissias2014sybil}.

@@

Group signatures were first introduced by Chaum and van Heyst, 1991,~\cite{Chaum1991} and then built upon by Rivest \textit{et al.}, 2001~\cite{Rivest2001}. The basis for anonymity in the CryptoNote protocol, however, is a slightly modified version of the \textit{Traceable ring signature} algorithm by Fukisaki and Suzuki, 2007~\cite{Fujisaki2007}. The algorithm allows a member of a group to send a transaction in such a way that it is impossible for a receiver to know any more about the sender than that it came from a group member without the use of a central authority.

@@

Additionally, if the receiver and sender have randomly generated, unique and new addresses, the Diffie-Hellman protocol can be used to generate a new pair of public-private keys. This is how untraceability of public keys is achieved. The sender should generate ephemeral keys for each transfer, enabling only the receiver to recover the corresponding private key. As an illustrative example, in Figure \ref{fig:ringsigs}, a schematic diagram shows households A, B and C signing a transaction since they are part of the same ring. A ring would, in reality, be many more households, not necessarily of the same microgrid. Let's assume that A is the true origin of the transaction. When E receives the transaction, the only thing that E can know with certainty is that one of A, B or C initiated the transaction. To increase the transaction anonymity further, a second, third or n rounds of ring signatures can be algorithmically imposed upon the network. With each round of signing parties, the group of potential origins grows linearly. Notably, the ring signature algorithm by Fujisaki and Suzuki, \cite{Fujisaki2007}, has been published in a peer-reviewed paper. This can be compared favorably to many cryptocurrency protocols which are simply published as white papers without any formal review-process~\cite{cryptonote}.
In practice, a transaction using the mixing service should be performed in the following way to ensure anonymity:

@@

\subsubsection{Mixing through Zero-Knowledge Proofs}
Zero-knowledge proofs (ZKP) are ways for a person to prove the knowledge of some specific fact to a verifier, without actually having to disclose the knowledge. Blum \textit{et al.} provided non-interactive ZKPs (NIZK) in 1988 \cite{Blum:1988:NZA:62212.62222}, where the prover and verifier don't have to interact or communicate directly with each other. The Zerocoin protocol \cite{miers2013zerocoin} outlines a way how NIZKs can achieve the untraceability objective of the previous section and it ensures that no double-spending is allowed.\footnote{Each coin in the protocol is identified uniquely by a serial number.} Zerocoin is a protocol for the decentralized mixing of coins, so that they can not be traced, or \textit{tainted}. However, senders and destinations can still be identified~\cite{miers2013zerocoin}.  Luckily, Zerocash~\cite{Sasson:2014:ZDA:2650286.2650810} extends the NIZK functionality to allow for anonymous transactions, anonymous balances and coins, improved performance of transactions and sending of assets to a receivers fixed address without action required from the receiver. Zerocash makes use of a more efficient version of the NIZK, used in Zerocoin, called ZK \textit{Succinct Non-interactive ARguments of Knowledge} (zk-SNARK). 
% It features the algorithms: \textbf{Setup($1^\lambda$)}$\rightarrow \textit{params}$, \textbf{Mint(}\textit{params})$\rightarrow \textit{(c,skc)}$, \textbf{Spend}(\textit{params, c, skc, R, \textbf{C}})$\rightarrow(\pi, S)$ and \textbf{Verify}(\textit{params, $\pi$, S, R, \textbf{C}})$\rightarrow$$\{$0,1$\}$. The \textbf{Setup} function takes a secret parameter and returns a global public set of parameters and description of the set of coins. It is only executed once in the lifetime of the scheme, and the authors of the protocol recommend the usage of a trusted party for this. \textbf{Mint} is used to create coins from the coin set, given the parameters. \textbf{Spend} and \textbf{Verify} are executed by a sender and a receiver, respectively at the beginning and end of each transaction.

@@

\subsubsection{Threats and weaknesses in Ring Signature- and Zero-Knowledge Proof-schemes}
\label{transthreat} 
\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{ringsigs.png}
\caption{Visualization of untraceability in ring signatures in smart meter-based energy trading and the potential deductions of origin of the transaction by a single household in the chain of signatures.}\label{fig:ringsigs}
\end{figure}
When applying either ring signatures or zero-knowledge SNARKs to PETra, potential weaknesses or attacks need to be considered.A potential threat to ring signatures is when a large amount of the unspent transactions are owned by an adversary or when insufficient amounts of signatures are included in a ring. When a prosumer A wishes to select a group of signatures to sign her transaction as well, then it is likely that she will select many of the transactions from the adversary. Assuming the adversary spends his outputs without \textit{mixing}\footnote{The number of other signatures used in the ring.}, then A's transaction is exposed as well~\cite{monero2014}. Recent research  also show that up to 65\% of Monero transactions are trivially traceable using one attack. They also exposes two more attacks that have been amended in the latest versions of the protocol, lowering the amount of transactions traceable to 20\%~\cite{monero2014,DBLP:journals/corr/MillerMLN17}.

One of the main weaknesses of the Zerocash-based protocol is that for each private transaction, a costly zk-SNARK needs to be computed. But that is not a threat to anonymity, just a practical reason why it might be difficult to run the scheme over a congested public blockchain. In \cite{Sasson:2014:ZDA:2650286.2650810}, experiments show an average time of 3 min to create the zk-SNARK for a private transaction, verifying it takes only 8.5 ms. Another large practical drawback of Zerocash is the lack of programmability and functionality that would be required in PETra. Zhang \textit{et al.} solve some of the practical flaws and amend security issues~\cite{zhangz}.
